Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-23 finnormal-nodalida-2015/finnormal2015.tex
bokmål
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58536 72bbbca6-d526-0410-a7d9-f06f51895060
more stuffs on the paper
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58538 72bbbca6-d526-0410-a7d9-f06f51895060

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration CITEXXX is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokmål and Norwegian Nynorsk \cite{unhammer2009}.

@@

We trained models based on two approaches, the first being phrase-based machine translation
CITEXXX and the second on character-based machine translation \cite{nakov2012}.

CBMT: \cite{TiedemannEAMT2009, TiedemannEACL2012}

@@

\newcite{nakov2012}

>>>>

There are a number of areas of research related to the task of text normalisation. Text
proofing tools, such as spelling and grammar checkers CITEXXX can be used to encourage adherence
to particular orthographic or grammatical norms. Accent and diacritic restoration CITEXXX is similar
in that it aims to bring text closer to standard orthography in order to facilitate treatment by 
automatic tools. Another related area is machine translation between different written norms of 
the same language. For example between Norwegian Bokm\aa{}l and Norwegian Nynorsk \cite{unhammer2009}.

@@

We trained models based on two approaches, the first being phrase-based machine translation
CITEXXX and the second on character-based machine translation \cite{nakov2012,TiedemannEAMT2009}.

@@

\newcite{nakov2012} present a method of statistical machine translation on the character level between related languages that takes advantage of phrase-based machine translation architecture. The method relies on preprocessing the input and output by inserting spaces in between the characters of words, for example the string `M\"{a} meen Helsinkiin' would become `M \"{a} \$ m e e n \$ H e l s i n k i i n' with a unigram model, or `M\"{a} \$ me en \$ He ls in ki in' with a bigram model.
